Something About Ground Based Asteroseismology

### 2017-09-11 paper/aldebaran.tex
small changes before I go to bed
fix maths
acknowledgements stub

\documentclass[modern]{aastex61}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\usepackage{natbib}
\usepackage{graphicx}
\usepackage{xspace}

@@

@@

@@

The halo photometry method proceeds as in \citet{White2017}. \textcolor{red}{More text here to explain in words.}
The flux $f_i$ at each cadence $i$ is constructed as a weighted sum of pixel values $p_{ij}$:

>>>>

\documentclass[modern]{aastex61}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\usepackage{natbib}
\usepackage{graphicx}
\usepackage{xspace}
\usepackage{amsmath}
\usepackage{amssymb}

@@

If we apply nonlinear statistical inference methods...

@@

This research has made use of the SIMBAD database, operated at CDS, Strasbourg, France, and NASA's Astrophysics Data System. The \kepler data presented in this paper were obtained from the Mikulski Archive for Space Telescopes (MAST). STScI is operated by the Association of Universities for Research in Astronomy, Inc., under NASA contract NAS5-26555. Support for MAST for non-HST data is provided by the NASA Office of Space Science via grant NNX13AC07G and by other grants and contracts.  This work made use of the IPython package \citep{PER-GRA:2007} This research made use of SciPy \citep{jones_scipy_2001};  \textsc{matplotlib}, a \textsc{Python} library for publication quality graphics \citep{Hunter:2007}; \textsc{Astropy}, a community-developed core \textsc{Python} package for astronomy \citep{2013A&A...558A..33A}; and \textsc{NumPy} \citep{van2011numpy}. Some of the acknowledgements were compiled using the Astronomy Acknowledgement Generator.

@@

The halo photometry method proceeds as in \citet{White2017}, with only minor changes. \textcolor{red}{More text here to explain in words.}
The flux $f_i$ at each cadence $i$ is constructed as a weighted sum of pixel values $p_{ij}$:
